Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-25 draft.tex
small edit

\begin{proof}
\owen{Essentially, we verify that a bunch of "forgetful functors" are $E_n$-monoidal.}
\end{proof}

>>>>

\begin{proof}
By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules. 
Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} (see also Example 3.4.4.7 of the same reference) $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
In other words, there is an object $\Bar{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ which gets sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.

Given a map of $E_n$-algebras $f : A \to B$ there is an $E_n$-monoidal functor of $E_n$-module categories 
\[
f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
\]
In particular, for $A = \UU_n \fg$, we see that the $E_n$-algebra $B$ defines an $E_n$-algebra object $f^*\Bar{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$. 
Again, the image of this object under the forgetful functor to $\Ch_k^{\otimes_k}$ is $B$.

Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1} A} \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}

Finally, restriction along the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$ defines monoidal functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
The desired $E_n$-algebra object $B_f$ is $i^* f^* \Bar{B}$.
\end{proof}
